\documentclass [11pt, letterpaper] {article}
\input {headings}
\newcommand \recipeName {White Rice}
\chead {\recipeName}

\begin {document}
\input {title}

White rice is an everyday dish in Brazil. In many parts of Brazil garlic is added to white rice. But not in the South. Thus we will follow the South tradition and leave the garlic out. The recipe here is for one cup of rice which serves three people. When scaling up the recipe, scale the water and rice amount linearly, but do not scale the salt linearly. You also will have to experiment with the cooking time for larger amounts.

\vspace{0.3in}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item	1 cup of rice
	\item 2 cups of water
	\item 1 1/2 Tbs of Canola oil
	\item 1 tablespoon of salt
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}
	\item {\bf Sautee and boil the rice}
	\begin{itemize}
	\item Heat the water in the microwave until it is boiling --- four to five minutes.
	\item Meanwhile in a small saucepan put the cooking oil and the rice and cook under high heat stirring constantly until the grains of rice start turn opake.
	\item Reduce the fire to the slowest simmer.
	\item Pour the hot water over the rice stirring.
	\item Cover the pot and simmer for 20 minutes. Do not open the pot.
	\item After 20 minutes, turn off the fire and keep the pot closed for another five minutes.
	\item Do not stir the rice. You can gently fluffy it up with a fork.
	\end{itemize}
	
	\end{enumerate}
\end{description}
\end{document}



