\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Bacon-Cheese Bread}
\chead{\recipeName}

\begin{document}
\input{title}

\begin{flushright}
{\bf From America's Text Kitchen}
\end{flushright}
 
 
\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 3 oz of Parmesan cheese, shredded on large holes of box grater (about 1 cup)
	\item 5	slices bacon (about 5 ounces), cut into ?-inch pieces
	\item 1/2	medium onion, minced (about 1/2 cup)
	\item 3	cups unbleached all-purpose flour (15 ounces)
	\item 1	tablespoon baking powder
	\item 1/4 	teaspoon cayenne pepper
	\item 1	teaspoon table salt
	\item 1/8	teaspoon ground black pepper
	\item 4	oz Gruyere cheese, cut into ?-inch cubes, or mild Asiago, crumbled into ?- to ?-inch pieces (about 1 cup)
	\item 1 1/4 	cups whole milk
	\item 1	large egg, beaten lightly
	\item 3/4 	cup sour cream
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf }
	\begin{itemize}
	\item Adjust oven rack to middle position; heat oven to 350 degrees. Spray 5 by 9-inch loaf pan with nonstick cooking spray, then sprinkle 1/2 cup Parmesan evenly in bottom of pan.

2. Fry bacon in medium nonstick skillet over medium heat, stirring occasionally, until browned and crisp, about 8 minutes. Using slotted spoon, transfer bacon to paper towel-lined plate and pour off all but 3 tablespoons bacon fat from skillet. Add onion to skillet and cook, stirring frequently, until softened, about 3 minutes; set skillet with onion aside.

3. In large bowl, whisk flour, baking powder, cayenne, salt, and pepper to combine. Using rubber spatula, mix in Gruyere, breaking up clumps, until cheese is coated with flour. Add bacon and onion mixture and stir to combine. In medium bowl, whisk together milk, egg, and sour cream. Using rubber spatula, gently fold wet ingredients into dry ingredients until just combined (batter will be heavy and thick). Do not overmix. Scrape batter into prepared loaf pan; spread to sides of pan and level surface with rubber spatula. Sprinkle remaining ? cup Parmesan evenly over surface.

4. Bake until deep golden brown and toothpick or skewer inserted in center of loaf comes out clean, 45 to 50 minutes. Cool in pan on wire rack 5 minutes; invert loaf from pan and continue to cool until warm, about 45 minutes. Cut into slices and serve.


        \item 
	\item 
	\end{itemize}
	\item {\bf }
	\begin{itemize}
	\item 
	\item 
	\end{itemize}
	\item {\bf }
	\begin{itemize}
	\item 
	\end{itemize}
	\item {\bf }
	\begin{itemize}
	\item 
	\item 
	\item 
	\item 
	\end{itemize}
	\item {\bf }
	\begin{itemize}
	\item 
	\item 
	\end{itemize}
	\item {\bf }
	\begin{itemize}
	\item 
	\item 
	\end{itemize}
	\item {\bf }
	\begin{itemize}
	\item 
	\end{itemize}
	\end{enumerate}

\end{description}
\end{document}



