\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Baked Pears}
\chead{\recipeName}

\begin{document}
\input{title}

\begin{flushright}
{\bf From {\it Lidia's Italian-American Kitchen} by Lidia M. Batianich}
\end{flushright}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 8 ripe but firm Bosc pears
	\item 4 cups of seedless red grapes
	\item 1 cup of sugar
	\item 1 1/3 cup of Moscato or other fruity white wine
	\item Juice of 2 lemons
	\item 2 tablespoons of apricot jam
	\item 1 tablespoon of vanilla extract
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Preheat the oven to 375 F}
	\item {\bf Prepare the grape bed}
	\begin{itemize}
	\item Remove the grapes from the steams.
        \item Wash the grapes well under cold water, rubbing them gently, and draining well. Washing the grapes well is important to remove the natural yeast from the skins of the grapes (it is a whitish power). After washed, the grapes will look darker.
	\item Place the grapes in a baking dish.
	\end{itemize}
	\item {\bf Mix the flavourings}
	\begin{itemize}
	\item Stir the sugar, Moscato, lemon juice, apricot jam, and vanilla together in a dish.
	\item Pour the mixture over the grapes
	\end{itemize}
	\item {\bf Prepare acciddulated water}
	\begin{itemize}
	\item Mix the juice of one lemon in large bowl of water.
	\end{itemize}
	\item {\bf Prepare the pears}
	\begin{itemize}
	\item Wash the pears, drain well.
	\item Cut each pear in four pieces lengthwise.
	\item Remove the core, seeds and stems.
	\item As each pear quarter is ready, drop it in the acidulated water to prevent it from browning.
	\end{itemize}
	\item {\bf Bake the pears}
	\begin{itemize}
	\item Remove the pear quarters from the acidulated water, drain well, and nestle them on the bed of grapes, cut side up.
	\item Bake, uncovered, until the pears are tender and the liquid around the grapes is thick and syrupy (about 50 minutes to 1 hour).
	\end{itemize}
	\item {\bf Reduce the syrup}
	\begin{itemize}
	\item Remove the pears and grapes from the dish with a slotted spoon.
	\item Cook down the sauce on top of the stove until the sauce becomes syrupy.
	\end{itemize}
	\item {\bf Serving}
	\begin{itemize}
	\item Serve the pears with grapes warm with a spoon of vanilla flavoured whipped cream.
	\end{itemize}
	\end{enumerate}
\end{description}
\end{document}





