\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Baked Apples with Dried Fruits}
\newcommand \fileName {BakedApples}
\chead{\recipeName}

\begin{document}
\input{title}

The exact amounts are not very important for this recipe. Variations in the fruit also work well. If preparing a vegan version, omit the butter. 

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 8 Granny Smith green apples
	\item 2 sticks of cinnamon 
	\item 1/2 cup of chopped Medjool dates
	\item 1/2 cup of chopped prunes 
	\item 1/2 cup of golden raisins
	\item 1/4 cup of brown sugar
	\item 1/2 cup of white wine
	\item 1 lemon
	\item optional: 1 cup of seedless grapes
	\item optional: 3 tablespoons of butter
	\end{itemize}

\item[Equipment:]\ \\
	\begin{itemize}
	\item Heavy bottom dish that can go into the oven
	\item microplane grater
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}	
	\item {\bf Pre-heat oven to 375 F}
	\item {\bf Zest the lemon and peel the apples}
	\begin{itemize}
	\item Using the microplane grater, zest the lemon making sure to not remove the white membrane and reserve.
	\item Cut each apple into four pieces, remove the core and peel each quarter. 
	\item Cut each quarter in half and add to the baking dish.
	\item Squeeze the lemon over the apple pieces, pulverize with the brown sugar and mix well.
	\end{itemize}
	\item {\bf Add cinnamon and dried fruit}
	\begin{itemize}
	\item Break each cinnamon stick into two pieces and add to the apples.
	\item Add diced dates, prunes, and the raisins. 
	\item Add grapes if using.
	\item Pour white wine.
	\item Add the lemon zest.
	\item Toss well.
	\item If using the butter, cut it in small pieces and distribute on top.
	\end{itemize}
	\item {\bf Bake the apples}
	\begin{itemize}
	\item Make for 45 min to 1 hour until the apples are tender.
	\item Remove from oven and let it cool for about 10 minuest.
	\item Toss gently with a spoon and serve.
	\end{itemize}
	\end{enumerate}
\end{description}
\end{document}
