\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Daniel's Banana Chocolate Cake}
\chead{\recipeName}

\begin{document}
\input{title}

{\hspace{2in} Adapted from Better Homes and Gardens Cookbook}

\vspace{0.5in}

This is my own adaptation of a traditional banana cake. I made it dairy free and added chocolate as a flavouring.
\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 3 ounces (85 gr) of dark chocolate
	\item 1/2 cup (3 1/2 ounces =  100 gr) of shortening
	\item 1 1/2 cups (11 oz = 310 gr) sugar
	\item 1 cup of mashed ripe bananas (about 3 = 13 oz = 360 gr)
	\item 2 eggs
	\item 1 teaspoon vanilla
	\item 1/2 teaspoon salt
	\item 3/4 cup (6 1/4 oz = 180 gr) of almond milk 
	\item 1 tablespoon of lemon juice
        \item 2 1/4 cup (11 1/2 oz = 320 gr) of all-purpose flour
	\item 1 1/2 teaspoons baking powder
	\item 1 teaspoon baking soda
	\end{itemize}
	
\item[Ingredients (optional chocolate glaze):]\ \\
	\begin{itemize}
	\item 4 ounces bittersweet chocolate
	\item 4 tablespoons unsalted butter
	\item 2 tablespoons corn syrup
	\item 1 teaspoon vanilla extract
	\end{itemize}
	
\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Prepare tube pan and heat oven}
	\begin{itemize}
	\item Spray or smear with shortening the pan, then dust with either flour or cocoa powder.
	\item Pre-heat oven to 350 F
	 \end{itemize}
	\item {\bf Chocolate Mixture}
	\begin{itemize}
	\item Melt chocolate and shortening in microwave in a large glass or heavy duty plastic bowl
	 \item Add sugar and mix
	 \item Add mashed bananas and mix
	 \item Add eggs and mix
	 \item Add vanilla and salt
	\end{itemize}
	\item {\bf Faking buttermilk}
	\begin{itemize}
        		\item In a measuring cup mix almond milk with lemon (it may separate).
	\end{itemize}
	\item {\bf Dry mixture}
	\begin{itemize}
	\item In a separate bowl mix flour, baking powder and baking soda
       	\end{itemize}
	\item {\bf Finishing the mixture}
	\begin{itemize}
        \item Add 1/3 of flour mixture to the chocolate mixture and stir until incorporated
        \item Add 1/3 of the milk mixture and stir until incorporated
        \item Repeat two more times until all the flour and milk are incorporated
        \end{itemize}
        \item {\bf Baking the cake}
	\begin{itemize}
        \item Pour cake batter into prepared pan
        \item Bake for 30 minutes (or longer) until a toothpick inserted into the cake comes out clean.
        \end{itemize}
        \item {\bf Cool and unmold the cake}
        \begin{itemize}
        \item Let the cake cool until is is just warm.
        \item Run a knife around the edges of the pan to release the cake.
        \item Invert in a clean cutting board (cake will be upside down).
        \item Put a platter at the bottom of the cake and invert into the plate (if planning to glaze the cake invert it on a wire rack and put the wire rack over a large baking pan.
        \end{itemize}
        
         \item {\bf Glaze the cake (optional)}
       	\begin{itemize}
        \item In bowl set over pot of simmering water, melt chocolate with butter and whisk until smooth. Remove bowl from pot, add corn syrup and vanilla, and mix until smooth and shiny. 
        \item Spread the glaze over the cake and let cool.
        \end{itemize}
     	\end{enumerate}         
\end{description}
\end{document}



