\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Beets and Cumin Salad}
\chead{\recipeName}

\begin{document}
\input{title}

This salad is by Tess Mallos in {\it The food of Morocco: a journey for food lovers}. I adopted the recipe to roast the beets instead of boiling them and I pickled the red onions to reduce their pungency. Also, I borrow a technique from India from raita and freshly toast the cumin seeds, crushing half of them and keeping the other half whole to sprinkle on top at the end.

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 6 beets
	\item 1/3 cup of olive oil
	\item 1 tablespoon of red wine vinegar
	\item 1 teaspoons of cumin seeds
	\item 1 \href{PickledRedOnions.html}{pickled red onion}
	\item 2 tablespoons of chopped flat-leaf parsley
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Prepare the beets}
	\begin{itemize}
	\item Heat oven to 350 degrees. 
	\item Wash the beets well.
	\item Wrap beets in foil or brush with olive oil and place in small roasting pan. 
	\item Roast until beets can easily be pierced with thin knife or trussing needle, about 1 hour for small to medium beets. 
	\item Cool slightly and remove skins --- wear latex gloves.
	\item Cut the tops and trim the roots.
	\item Halve the beets, cut in slender edges.
	\end{itemize}
	\item {\bf Dress the beets}
	\begin{itemize}
	\item Put the cumin seeds in a dry cold skillet.
	\item Put the skillet over moderate heat and gently toast the cumin seeds until they are fragrant.
	\item Remove from the heat and immediately transfer the seeds to a small cool glass bowl to stop their cooking.
	\item Transfer half of the toasted seeds to a wooden cutting board.
	\item Using the bottom of a small cold pan crush the seeds on the cutting board until they are finely crushed.
	\item In a deep bowl, beat the olive oil with the red wine vinegar, the crushed cumin and a good grinding of black pepper.
	\item Add the beet wedges to the dressing and stir well.
	\item Add the parsley and toss well.
	\item Add the prickled onions and toss gently.
	\item Sprinkle with the 1/2 teaspoon of reserved toasted cumin seeds.
	\item Serve at room temperature.
	\end{itemize}
	\end{enumerate}
\end{description}
\end{document}
