\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Wine Cake}
\chead{\recipeName}

\begin{document}
\input{title}

This is a recipe passed to me by my mother Dioraci Urtassum.

\begin{description}

\item[Ingredientes:]\ \\
	\begin{itemize}
	\item 6 eggs
	\item 3 cups of sugar (21 oz)
	\item Grated zest from one orange
	\item 1/2 teaspoon of salt
	\item 1 1/2 cup of dry white wine (12.5 oz)
	\item 1 1/2 cup of flavourless cooking oil (11 oz)
	\item 4 cups of all-purpose flour (20 oz)
	\item 4 teaspoon of baking powder
	\end{itemize}
	
\item[Ingredientes (glaze):]\ \\
	\begin{itemize}
	\item 1 cup of sugar
	\item 1/2 cup of rum or cognac 
	\end{itemize}
	
\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Pre-heat oven to 325 F.}
	\item {\bf Prepare three or four loaf pans}
	\begin{itemize}
	\item Spray the pans with cooking spray.
	\item Cut a piece of parchment paper to cover the bottom and the narrow sides of each pan.
	\item Place the paper in the pan and spray the paper
	 \end{itemize}
	\item {\bf Mix the batter}
	\begin{itemize}
	\item Mix the eggs with the sugar in a large bowl.
	 \item Add the lemon zest, salt, wine, cooking oil and mix well.
	 \item Put all the flour on top and put the baking power on top of the flour.
	 \item First gently mix the baking powder only with the flour on top of the wet ingredients.
	 \item Then mix the batter until it is homogeneous
	\end{itemize}
	\item {\bf Bake the bolos}
	\begin{itemize}
        		\item Divide the batter into the prepared pans.
		\item Bake in the middle rack. After 20 minutes rotate the pans.
		\item The bolos should be baked in about 40 minutes.
		\item Test by inserting a toothpick into the bolo. It should come out mostly clean.
	\end{itemize}
        
         \item {\bf Glaze}
       	\begin{itemize}
        \item Measure the 1 cup of sugar and carefully dump into the center of a small sauce pan.
        \item Carefully dump 1/2 cup of water around the sugar. 
        \item Take the pan to the stove and cook in moderate heat until all the sugar dissolves --- only stir carefully to not splash the sides of the pan if needed after the mixture is already very hot.
        \item Let the mixture cook until it forms a very thick sirup --- you may wish to let it caramelize a bit, but only to a light amber colour.
        \item Add 1/2 cup of rum or cognac and stir with the thick sirup until it is completely homogeneous.
        \item As soon as you remove the bolos from the oven, prickle the top with a toothpick and divide the glaze amongst the bolos.
        \item Let the glaze soak into the bolos for about 15 minutes.
        \item Invert the bolos into a clean cutting board and place them top-side up on a cooling rack.
         \end{itemize}
     	\end{enumerate}         
\end{description}
\end{document}



