\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Brutti Ma Buoni}
\chead{\recipeName}

\begin{document}
\input{title}

\begin{flushright}
{\bf From {\it Essentials of Classic Italian Cooking} by Marcella Hazan}
\end{flushright}

This is are Piedmontese Almond Cookies. The name translates to ``ugly but good" and indeed they are delicious.

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 11 ounces of blanched and skinned almonds
	\item 1 1/4 cup of sugar
	\item 4 egg whites
	\item salt
	\item 1 teaspoon of vanilla extract
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Preheat the oven to 300F}
	\item {\bf Pulverize the almonds}
	\begin{itemize}
	\item Mix the almonds with 1/4 cup of sugar in the bowl of a food processor..
        \item Process until you obtain a fine mixture, do not overprocess or you will end up with almond butter.
	\end{itemize}
	\item {\bf Prepare the merengue}
	\begin{itemize}
	\item Bring with about 2 inches of water to a boil.
	\item Place the egg whites and 1/2 a cup of sugar in the bowl of a mixer.
	\item Reduce the fire to keep the water at a fast simmer.
	\item Place the bowl over the water, stir constantly until you place your clean finger on the egg white and sugar mixture and feel that it is definitely warm.
	\item Beat the mixture in the mixer until you obtain firm peaks.
	\item Add the vanilla extract and the final 1/2 cup of sugar and beat for another 30 seconds.
	\end{itemize}
	\item {\bf Fold the almonds}
	\begin{itemize}
	\item Fold the pulverized almonds into the merengue with a rubber spatula.
	\end{itemize}
	\item {\bf Bake the cookies}
	\begin{itemize}
	\item Grease and lightly dust with flour a cookie sheet.
	\item Place a piping bag, without the tip, over a large glass, folding the large end backwards around the glass rim.
	\item Feel the bag with the merengue batter.
	\item Pipe small round cookies in the baking sheet.
	\item If the cookies have a little tip, fold a clean kitchen towel, wet it and press it with your hands to remove excess water.
	\item Holding both ends of the folded towel, gently touch the top of the cookies to flatten the tips.
	\item Bake for bout 30 minutes (or longer), until they acquire a very light brown color.
	\item Remove from the stove and let them cool for a minute or two.
	\item Gently remove them from the baking sheet and spread them over cooling racks.
	\item After they are completely cool, store in air-tight containers.
	\end{itemize}
	\end{enumerate}

\end{description}
\end{document}




