\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Crispy Creamy Spinach}
\chead{\recipeName}

\begin{document}
\input{title}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 1 lb of fresh spinach
	\item 2 tablespoon of shallots finely diced
	\item 1/4 cup of cream
	\item 1 1/2 cup of fresh bread crumbs
	\item 1/4 cup of melting cheese (fontina)
	\item 2 tablespoons of butter
	\item nutmeg
	\item white pepper
	\item 3 tablespoons of olive oil
	\item large pinch of dried thyme
	\item salt freshly ground black pepper
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Make the bread crumbs}
	\begin{itemize}
	\item Put the fresh bread in a food processor e process until you obtain the bread crumbs
	\end{itemize}
	\item {\bf Blanch the Spinach}
	\begin{itemize}
	\item Boil a large pot of water.
        \item Remove bigger stems from the spinach leaves and wash it throughly
	\item Dump the clean spinach in the boiling water.
	\item After 2 minutes, remove the spinach to a pasta drainer, and let it drain until water stops dripping from it.
	\end{itemize}
	\item {\bf Saute the Spinach}
	\begin{itemize}
	\item Melt the butter in a non-sticking frying pan.
	\item Add the finely diced shallots and cook until softened (2-3 minutes).
	\item Add the spinach and saute for several minutes stirring with a wooden spoon.
	\item When most of the residual water in the spinach has evaporated, add the cream.
	\item Add several grindings of nutmeg, and a pinch of white pepper.
	\item Simmer for a few minutes until the cream start to thicken.
	\item Turn off the heat.
	\item Add 1/2 a cup of fresh bread crumbs and stir.
	\item Add the grated melting cheese
	\end{itemize}
	\item {\bf Prepare the Bread Topping}
	\begin{itemize}
	\item Season the remainder fresh bread crumbs with salt, black pepper and dried thyme, and the olive oil.
	\end{itemize}
	\item {\bf Bake the Spinach}
	\begin{itemize}
	\item Oil or butter individual dishes (or a large casserole)
	\item Distribute the spinach into the plates
	\item Top with the seasoned bread crumbs
	\item Bake for about 12-15 minutes at 400 degrees
	\item Let it cool for 5 minutes before serving
	\end{itemize}
	\end{enumerate}
\end{description}
\end{document}
