\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Pressure-Cooker Curry}
\chead{\recipeName}

\begin{document}
\input{title}

This is a recipe published by Jacques Pepin in the 
\href{http://legacy.sandiegouniontribune.com/uniontrib/20081015/news_1f15pepin.html}{San Diego Union Tribune} on October 15 2008. This is a great weeknight recipe. The preparation is simple and the result is delicious. I have made this recipe with lamb, with beef and with pork. Use  beef chuck, pork shoulder, or a shoulder or leg of lamb.

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 2 pounds of meat (lamb, beef, or pork) cut in one-inch cubes
	\item 2 cups diced onions (1-inch pieces)
	\item 3 tablespoons coarsely chopped garlic
	\item 1 1/2 cups coarsely diced tomatoes
	\item 1 apple, cored but not peeled, cut into 1-inch pieces
	\item 1 banana, peeled and sliced
	\item 1 tablespoon chopped jalape–o or to taste
	\item 1 cup coconut milk, well-stirred
	\item 2 1/2 tablespoons curry powder, or more to taste
	\item 1 teaspoon ground cumin, or more to taste
	\item 1 teaspoon salt
	\item 2 bay leaves
	\item 1/2 cup fruity white wine
	\item 2 tablespoons instant flour, such as Wondra
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf }
	\begin{itemize}
	\item Put the meat, onions, garlic, tomatoes, apple, banana, jalape–o, coconut milk, curry powder, cumin, salt, bay leaves and wine into a pressure cooker. 
	\item Sprinkle the flour on top and mix well.
	\item Bring to a boil over high heat. Secure the lid on the pressure cooker and cook over high heat until 15 pounds pressure (high pressure, if your cooker does not register pounds) is reached. 
	\item Reduce heat and cook for 25 minutes, maintaining desired pressure.
	\item Decompress the pressure cooker according to the manufacturer's instructions; remove the lid. 
	\item Remove and discard bay leaves. 
	\item Taste and adjust seasonings if necessary. Ladle over rice.
	\end{itemize}
	\end{enumerate}

\end{description}
\end{document}



