\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Feij\~ao Preto}
\chead{\recipeName}

\begin{document}
\input{title}

In most of Brazil beans and rice is an everyday staple.
In the Southeast of Brazil everyday beans are brown beans such as pinto beans or kidney beans. Black beans are reserved for a special Saturday meal, served in many restaurants in Rio de Janeiro, called {\it Feijoada}. But in the South of Brazil the everyday beans are the black beans. Here we are preparing this everyday version of the dish as it is usually done in Rio Grande do  Sul. In Edmonton the best place for smoked meats for the beans is K\&K Foodliner on Whyte Ave. A nice tip is to ask for smoked bones, which are much less expensive and have lots of meat on them. K\&K also has great smoked bacon. The best place to buy black beans in Edmonton is the Italian Centre. It is important to mash the beans with a fork rather than using a blender or food processor because you do not want the skins of the beans to be triturated by a machine.

\vspace{0.3in}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item	2 pounds of black beans
	\item 1 1/2 to 2 pounds of smoked pork
	\item 2 bay leaves 
	\item 1/2 pound of sliced smoked bacon 
	\item 1 large onion finelly diced
	\item 1/2 teaspoon of sugar
	\item 2 garlic cloves
	\item 1 Tbs salt
	\item 1 small red pepper (pimenta de cheiro)
	\item 1/2 Tbs of cumin
	\item Freshly ground black pepper
	\item 1/2 Tbs of lemon juice
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}
	\item {\bf Washing and Soaking the Beans}
	\begin{itemize}
	\item Put black beans in a large bowl and cover with cold water, using your hands rub the beans to wash the preserving powder that had been added to the beans for storage.
	\item Pour beans and water in a colander or strainer over the sink to drain the beans.
	\item Repeat this washing process at least two more times.
	\item {\bf Quick Soaking Method} Put the pork meat and bay leaves in the pressure cooker, add the beans, cover with water so that there is about two inches of water over the beans, cover the pressure cooker and set over moderately high heat until it comes to pressure. Turn the fire off and let it rest for thirty minutes.
	\item {\bf Regular Soaking Method} Place beans in a bowl and pour water to cover the beans by about 2 inches. Let soak for at least 4 hours, and up to 16 hours, at room temperature.
	\end{itemize}
	
	\item {\bf Cook the beans}
	\begin{itemize}
	\item If using regular soaking method, now put the smoked pork and the bay leaves in the pressure cooker.
	\item Put the soaked beans into the pressure cooker.
	\item Pour enough water to cover the beans by at least one inch.
	\item Cover the pot and bring to a boil until steam starts escaping.
	\item Reduce the heat but ensure the steam is still escaping from the pressure cooker throughout the cooking time.
	\item Cook under pressure for thirty minutes. 
	\item You can either let it cool in the pressure cooker or you can put the pressure cooker under cold  running water, gently lifting the steam valve under the running water.
	\end{itemize}
	
	\item {\bf Season the beans}
	\begin{itemize}
	\item Peel the garlic and crush on a cutting board, put the salt over the garlic and crush to a paste. 
	\item Mince the red pepper and crush together with the garlic paste.
	\item Grind black pepper into the garlic paste and reserve.
	\item Cut onions into a fine dice.
	\item In a large heavy pan, put the 1 tablespoon of cooking oil, and place over moderately high heat.
	\item When warm, add the bacon, cut into 2-inch strips, and cook until most the fat is rendered, but you do not want the bacon to be very crisp.
	\item With a slotted spoon, remove the bacon pieces from the pan to a plate and reserve.
	\item Add the diced onions to the bacon fat and cook until they have a golden colour.
	\item Sprinkle the sugar over the onions and keep sauteeing until they take a mahogany colour.
	\item Push onions to the side of the pan to open a spot on the middle.
	\item Put the garlic paste and the ground cumin on the spot in the centre of the pan and stir for about 30 seconds --- you will smell the garlic and the cumin.
	\item Put some cold water into the pan to slow down the cooking.
	\item Return the bacon pieces to the pan.
	\end{itemize}	
	
	\item {\bf Mashing the beans}
	\begin{itemize}
	\item  Pour most of the liquid and some of the beans from the pressure cooker into the pan with the onions and garlic, make sure to hold back at least two cups of cooked beans.
	\item Place about one cup of the cooked beans in a dinner plate and mash them up with a fork. 
	\item Add the mashed beans to the pan with the remainder beans.
	\item Repeat with the second cup of cooked beans.
	\end{itemize}
	
	\item {\bf Finish cooking the beans}
	\begin{itemize}
	\item Cook the seasoned beans over moderate heat stirring from time to time.
	\item After it is cooked, turn off the heat and add the lemon juice.
	\end{itemize}
	\end{enumerate}
\end{description}
\end{document}



