\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Green Bean and Onion Salad}
\chead{\recipeName}

\begin{document}
\input{title}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 400gr of fresh green beans
	\item 2 \href{PickledRedOnions.html}{pickled red onions}
	\item 1 Tbs of fennel seeds
	\item Olive Oil
	\item Freshly Ground Black Pepper
	\item Rice Vinegar
	\item Fresh Basil
	\item 1/2 teaspoon of salt (or to taste)
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf French and Blanch the Green Beans}
	\begin{itemize}
	\item Cut off the end of each green bean.
	\item Cut in the diagonal into small pieces.
	\item Bring a large pot of water to a rapid boil.
	\item Fill a large bowl with cold water and add ice to the bowl.
	\item Drop all the green beans to the boiling water at once and cover the pot immediately so that it comes back to a boil quickly.
	\item Let it cook for about two minutes.
	\item Test a piece of green bean. It should be very firm still.
	\item Lift the green beans from the boiling water with a mesh.
	\item Drop them in the bowl of cold water.
	\item Let them cool completely in the cold water.
	\end{itemize}
	\item {\bf Assemble the Salad}
	\begin{itemize}
	\item Put the green beans in a large bowl.
	\item Season with olive oil, rice vinegar, salt, and pepper to taste.
	\item In a dry skillet warm up the fennel seeds until they are very fragrant.
	\item Remove to a plate and let them cool off completely.
	\item Add drained onions and fennel seeds to the green beans.
	\end{itemize}
	\end{enumerate}
\end{description}
\end{document}
