\documentclass [11pt, letterpaper] {article}
\input {headings}
\newcommand \recipeName {Carrot Hash}
\chead {\recipeName}

\begin {document}
\input {title}

{\it Guisadinho de verdura} is a hash made with vegetables and meat. Many different vegetables can be used. Carrots, green beans, peas and squash are typical. Usually the hash contains one, or at most two, vegetables. Here we use carrots and peas. A small amount of meat is used as flavouring. There is no pepper and no herbs, other than a bit of parsley in the end, in this dish. This allows the sweetness of the vegetables to come through. Typically the trims of piece of beef that was used for another dish are used here.

\vspace{.3in}
\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item	1 1/2 pound of carrots
	\item 1 teaspoon of salt
	\item 1 pound of frozen baby peas
	\item 1 large onion finally diced.
	\item 1 cup of finally diced beef
	\item 2 Tbs of cooking oil
	\item 1/2 cup of diced tomatoes
	\item 1 teaspoon of tomato paste
	\item salt
	\item Chopped parsley
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}
	\item {\bf Prepare the carrots}
	\begin{itemize}
	\item Peel the carrots.
	\item Cut the carrots lengthwise into 3/8 inch planks.
	\item Stack the planks and cut then into 3/8 x 3/8 inch batons.
	\item Stack the batons and cut them into 3/8 x 3/8 x 3/8 inches cubes. You are aiming to have the carrots cut into the size of a mature pea.
	\item Toss the carrots with 1 teaspoon of salt and let it stand for at least half hour.
	\end{itemize}

	\item {\bf Prepare the flavour base}
	\begin{itemize}
	\item In a heavy saucepan, heat up the oil.
	\item Add the diced beef and cook stirring frequently until it is throughly brown.
	\item Add the onions and cook until they start browning.
	\item Add the tomato paste and cook stirring for a minute until it starts browning.
	\item Add the diced tomatoes, stir and cook for a few minutes to reduce the water in the tomatoes.
	\end{itemize}
	
	\item {\bf Cook the vegetables}
	\begin{itemize}
	\item Add the diced carrots to the flavour base and add a small amount of water --- less than what would completely cover the carrots --- turn the heat to medium cover the pot and cook until the carrots are almost cooked but still firm.
	\item Rinse the frozen peas under cold water and add to the carrots.
	\item Cook under medium heat for a few more minutes.
	\item Taste for salt and adjust as needed.
	\item Remove from stove and add chopped parsley.
	\end{itemize}
	\end{enumerate}
\end{description}
\end{document}



