\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Indian Rice Salad}
\chead{\recipeName}

\begin{document}
\input{title}

I made this recipe in large quantities for our Summer Garden Party and it was a great success.


\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item	 8 3/4 oz basamati rice
	\item 17 fl oz hot water
	\item 1 3/4 oz slivered almonds
	\item 2 cloves
	\item 1/2 cup distilled white vinegar
	\item 1/6 cup sugar (find equivalent Tablespoons)
	\item 1/4 teaspoon salt
	\item 1 cinnamon stick
	\item 4 cardamon pods
	\item 2 Tablespoon vegetable oil
	\item 1 teaspoon saffron threads
	\item 1 teaspoon cumin seeds
	\item 1 teaspoon turmeric
	\item 1 teaspoon salt
	\item 1 bunch of fresh spinach
	\item Half a red onion, \href{PickledRedOnions.html}{thinly sliced and pickled}
	\item 2 Tablespoon cilantro, chopped
	\item the juice of 1 lime
	\item 2 Tablespoon olive oil
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}
	\item {\bf Perfume the oil}
	\begin{itemize}
	\item Place the saucepan with a lead in which you will cook the rice over medium heat and allow it to warm through. 
	\item Add the oil, cloves, cinnamon and cardamom. 
	\item Stir a bit and let the oil heat up, stirring occasionally. Once the spices begin to perfume the kitchen, remove them from the oil and discard.
	\end{itemize}
	
	\item {\bf Toast the slivered almonds }
	\begin{itemize}
	\item Heat oven to 300 F
	\item Spread slivered almonds onto a clean baking sheet
	\item Toast almonds until very lightly golden and they start to release their fragrance (15 to 20 minutes). Monitor closely as they can easily overcook and become bitter.
	\end{itemize}
	
	\item {\bf Cook the rice }
	\begin{itemize}
	\item Add the rice and the cumin to the perfumed rice stir to coat well.
	\item Add the turmeric and salt and stir them in. 
	\item Add the water and the saffron threads and bring it to a simmer. 
	\item Once simmering put the lid on and turn down the heat. 
	\item Let cook for 12 minutes. 
	\item Turn the heat off and leave the rice to cook for a further five minutes.
	\end{itemize}
		
	\item {\bf Fluff and cool the rice}
	\begin{itemize}
	\item Take the pan off the heat. 
	\item Use a fork fluff up the rice and spread it onto a baking sheet to cool down.
	\end{itemize}
	
	\item {\bf Assemble the salad}
	\begin{itemize}
	\item Transfer the rice to a large bowl. 
	\item Add the spinach, coriander, sliced onion, lime juice, olive oil and mix it all together well.
	\item Arrange into a serving dish and sprinkle the toasted almonds on top.
	\item Serve at room temperature.
	\end{itemize}

	\end{enumerate}
\end{description}
\end{document}



