\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Orange and Radish Salad}
\chead{\recipeName}

\begin{document}
\input{title}

This Moroccan salad is very different and surprisingly delicious. The key is to not mix the radishes with the orange and dressing until the very last minute.

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 3 sweet oranges 
	\item 12 red radishes
	\item 1 tablespoon lemon juice
	\item 2 teaspoons of sugar
	\item 2 tablespoons of olive oil
	\item pinch of salt
	\item 1 tablespoon of orange flower water
	\item ground cinnamon
	\item small mint leaves
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Prepare the oranges}
	\begin{itemize}
	\item Using a sharp knife, cut the bottom and top of each orange.
	\item Place each orange cut site down, and Cut the peel off from top to bottom ensuring to remove all traces of the pit and cutting through the outer membranes to explose the flesh.
	\item Holding each orange over a small bowl to catch the juices, segment them by cutting between the membranes.
	\item Remove any seeds from the orange segments.
	\item Put the segments in the bowl.
	\item Squeeze the remains of the orange into the bowl.
	\item Drain the orange segments using a large strainer.
	\item Return the orange segments to the the bowl, set the juices aside. 
	\end{itemize}
	\item {\bf Prepare the radishes}
	\begin{itemize}
	\item Wash the radishes and trim the roots.
	\item Either cut in thinly slices or in narrow strips using a mandolin.
	\item Keep the radishes in a dish covered with saran wrap.
	\item Keep it in the fridge until ready to serve.
	\end{itemize}
	\item {\bf Dress the orange}
	\begin{itemize}
	\item Put two tablespoons of the reserved orange juice in a small bowl. 
	\item Add the lemon juice, sugar, olive oil and a pinch of salt.
	\item Beat well and pour over the orange segments.
	\item Sprinkle with orange flower water, toss lightly, cover and chill for 15 minutes.
	\end{itemize}
	\item {\bf Serve}
	\begin{itemize}
	\item Toss the dressed orange segments with the radishes.
	\item Put in a serving bowl.
	\item Sprinkle lightly with cinnamon.
	\item Scatter with the mint leaves.
	\end{itemize}
	\end{enumerate}
\end{description}
\end{document}
