\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Daniel's Pancakes}
\chead{\recipeName}

\begin{document}
\input{title}


When Daniel was little we found out that he was lactose intolerant. We spend almost a year trying to figure out a way to make dairy-free pancakes for him. Our initial attempts to just replace milk for almond milk in the regular pancakes were disappointing. Eventually we got the consistency and flavour right by adding an additional egg yolk for additional richness and some extra sugar to compensate for the absent natural sweetness of the milk. But still, the pancakes would not brown properly. The solution was to replace the second teaspoon of baking power for 1/2 teaspoon of baking soda and a small amount of lemon juice. Finally we got the consistency, flavour, and colour right without using any dairy products. We have been executing this pancake recipes for about a decade now and it turns out right every time.
\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 1 egg + 1 yolk
	\item 1 1/2 Tbs of sugar 
	\item 1/2 teaspoon salt
	\item 2 Tbs (20 gr) cooking oil
	\item 1/2 Tbs lemon juice
	\item 1 cup+ (9 ? oz) unsweetened almond milk
	\item 1 cup (5 oz) flour
	\item 1 teaspoon baking powder
	\item 1/2 teaspoon baking soda
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}
	\item {\bf Mix the batter}
	\begin{itemize}
	\item In a bowl put the egg and the yolk, sugar, salt, cooking oil, lemon and stir well with a whisk.
	\item Add the almond milk and mix.
	\item Put all the flour on top of the wet ingredients (do not mix yet).
	\item Put the baking powder and the baking soda on top of the flour.
	\item First briefly gently mix the baking power and the baking soda with the flour still on top of the wet ingredients.
	\item Then mix all the ingredients until incorporated, but do not over mix otherwise the pancakes will be tough.
	\end{itemize}

	\item {\bf Cook the pancake}
	\begin{itemize}
	\item Heat up a griddle, or a cast-iron frying pan, or a non-sticking pan with a heavy button.
	\item When a few droplets of water sprinkled into the griddle "dance" around quickly and evaporate, the griddle is ready.
	\item Spray the griddle with baking spray and then wipe it with a paper towel.
	\item Pour several small amounts of the batter and let it cook until you see bubbles forming and see that they are golden in the underside when you gently lift it with a spatula and peek.
	\item Flip and cook on the underside.
	\item Spread a small mount of butter, or margarine, on the hot pancakes and serve immediately with maple sirup.
	\end{itemize}

	\end{enumerate}
\end{description}
\end{document}



