\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Passion Fruit Curd}
\chead{\recipeName}

\begin{document}
\input{title}

\begin{flushright}
{\bf Adapted from America's Test Kitchen Lemon Curd}
\end{flushright}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 1/3 cup of passion fruit juice
	\item 2 large eggs
	\item 1 egg yolk
	\item 1/2 cup sugar (3 1/2 ounces)
	\item 2 tablespoons unsalted butter, cut into 1/2-inch cubes and chilled
	\item 1 tablespoon heavy cream
	\item 1 pinch of salt
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Cook the curd}
	\begin{itemize}
	\item Heat the passion fruit juice in nonreactive saucepan over medium heat until hot but not boiling. 	
	\item In the bowl of a standing mix, beat the eggs and yolk; gradually whisk in sugar. 
	\item Slowly pour hot passion fruit juice into eggs.
	\item Pour the beaten eggs with juice into the still warm saucepan.
	\item Cook over medium heat, stirring constantly with wooden spoon, until mixture registers 170 degrees on instant-read thermometer and is thick enough to cling to spoon, about 3 minutes.
	\end{itemize}
	\item {\bf Add the cold ingredients and strain}
	\begin{itemize}
	\item Remove pan from heat and stir in cold butter until incorporated.
	\item Stir in cream and salt.
	\item  Pour curd through fine-mesh strainer into a nonreactive bowl. 
	\item Cover surface of curd directly with plastic wrap; refrigerate until needed.
	\end{itemize}
	\end{enumerate}

\end{description}
\end{document}
