\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Passion Fruit Cake}
\chead{\recipeName}

\begin{document}
\input{title}

This is another dairy-free cake recipe that I gotcd from my Mom in Brazil. In Edmonton we can find frozen passion-fruit pulp at Para\'iso Tropical, which is perfect for this cake. Make sure to bake the cake until a toothpick inserted in the middle comes clean so that it will not collapse later. Fro a dinner party, serve this cake with some \href{PassionFruitCurd.html}{Passion Fruit Curd}.

\vspace{0.3in}
\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 5 eggs
	\item 100 grams of unsalted butter
	\item 2 cups os sugar (350 grams)
	\item 2  1/2 cups of flour (300 grams)
	\item 1 Tablespoon of baking powder
	\item 1 cup of unsweetened passion-fruit juice
	\item 1/4 teaspoon of salt
	\end{itemize}

\item[Syrup Ingredients:]\ \\
	\begin{itemize}
	\item 1 cup of sugar
	\item 1 cup of unsweetened passion-fruit juice
	\end{itemize}

\item[Procedure:]\ \\
	\begin{itemize}
	\item Preheat oven to 350 F
	\item Spray a tube pan and pulverize it with sugar.
	\item Separate the eggs putting the egg whites in the bowl of a mixer and the yolks in a large mixing bowl.
	\item Using a whisk mix the egg yolks with the sugar.
	\item Add the passion-fruit juice to the yolks.
	\item Using a strainer, sift the flour and the baking powder onto the yolks and juice mix, in several batches, slowly mixing to avoid lumps. 
	\item Beat the egg whites to soft peaks.
	\item Dump the beaten egg whites into the batter and slowly fold with the whisk until homogeneous but not over mixed.
	 \item Pour in the prepared tube pan. 
	\item Bake until a toothpick inserted in the middle of the cake comes out clean.
	\item While it is baking, make a sirup by dumping the one cup of sugar on the centre of the bottom of a clean small saucepan. Pour the passion-fruit juice around the sugar and bring to a boil. This should be a thin syrup.
	\item Once the cake is baked, make several holes on the top with a toothpick and then pour the very warm syrup all over the cake.
	\item Let it cool slightly, but not for too long so that the syrup does not stick too hard to the pan.
	\item Run a sharp knife all over the pan to loosen it. Remove from the pan. 
	\end{itemize}
\end{description}
\end{document}
