\documentclass [11pt, letterpaper] {article}
\input {headings}
\newcommand \recipeName {Caramelized Pears with Blue Chese}
\chead {\recipeName}

\begin {document}
\input {title}

\begin{flushright}
From {\it America's Test Kitchen}
\end{flushright}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 1/3 cup of water
	\item 2/3 cup sugar  (4 3/4 ounces) 
	\item 3 ripe but firm bosch pears
	\item 2/3 cups of heavy cream
	\item table salt
	\item 1/4 teaspoon of coarse ground black pepper
	\item 3 ounces of blue cheese cut into wedges
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}
	\item {\bf Cook Pears}
	\begin{itemize}
	\item Place the water in a 12-inch nonstick skillet and pour the sugar into the center of the pan, taking care not to let the crystals adhere to the sides of the pan. Bring to a boil over high heat, stirring occasionally, until the sugar is fully dissolved and the mixture is bubbling wildly. 
	\item Add the pears to the skillet, cut-side down, cover, reduce the heat to medium-high, and cook until the pears are nearly tender (a paring knife inserted into the center of the pears feels slight resistance).
	\item Uncover, reduce the heat to medium, and cook until the sauce is golden brown and the cut sides of the pears are partly caramelized, 3 to 5 minutes. 
	\end{itemize}

	\item {\bf Make Caramel Sauce}
	\begin{itemize}
	\item Pour the heavy cream around the pears and cook, shaking the pan back and forth, until the sauce is a smooth, deep caramel color and the cut sides of the pears are beautifully golden, 3 to 5 minutes.
	\end{itemize}

	\item {\bf Seve }
	\begin{itemize}
	\item Remove the pan from the heat. Using tongs, carefully remove the pears from the pan and place cut-side up on a wire rack set over a trimmed baking sheet. 
	\item Cool slightly.
	\item Season the sauce left in the pan with salt to taste and the crushed black pepper, then pour it into a liquid measuring cup.
	\item Carefully (the pears will still be hot) stand each pear half upright on an individual plate and arrange a wedge of the blue cheese beside it.
	\item Drizzle the plate and some of the pear with the caramel sauce. Serve immediately. 
	\end{itemize}

	\end{enumerate}
\end{description}
\end{document}



