\documentclass [11pt, letterpaper] {article}
\input {headings}
\newcommand \recipeName {Chicken with Porcini and Tomatoes}
\chead {\recipeName}

\begin {document}
\input {title}
\begin{flushright}
{\hspace{4in} Adapted from Marcella Hazan.}
\end{flushright}
\vspace{0.5in}


Sometimes a dish is defined for what it does not have. This is one such dish. It is an Italian chicken with tomatoes that has no garlic, onions, herbs or olive oil. The simplicity of this dish is what makes it so attractive. Resist the temptation of even adding a bit of parsley to this recipe.

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item	4 pounds of Skinless boneless chicken thighs 
	\item 2 Tbs of vegetable oil
	\item Freshly ground black pepper
	\item 1/2 cup of dry white wine
	\item 1 ounce of dried porcini mushrooms
	\item Water from the mushroom soak
	\item 1/4 cup canned imported Italian plum tomatoes, chopped coarse, with their juice
	\item 1 tablespoon of butter
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}

	\item {\bf Salt the chicken}
	\begin{itemize}
	\item Lightly sprinkle salt on the chicken and let it rest for at least one hour, but up to 24 hours.
	\end{itemize}

	\item {Soak the mushroom}
	\begin{itemize}
	\item Put mushroom in a small dish.
	\item Add 3/4 cups of hot water.
	\item Cover the dish and let it rest for at least 10 minutes.
	\item Scoop the mushroom from the liquid and dice into small pieces.
	\item Reserve the liquid
	\end{itemize}
	
	\item {\bf Brown the chicken}
	\begin{itemize}
	\item Lightly dust the chicken pieces with flour
	\item Put oil a saut\'e pan, turn on the heat to medium high, and when the oil is very hot, slip the floured chicken pieces. Cook in one side until it is lightly brown, then turn and brown on the other side.
	\item Add the wine and let the wine simmer for 30 seconds while you scrape any browning bits from the pan.
	\end{itemize}

	\item {\bf Add mushroom and tomatoes }
	\begin{itemize}
	\item Add the chopped reconstituted mushrooms.
	\item Pour the mushroom-soaking water into the pot slowly being careful to not pour any solids that accumulate on the bottom of the dish.
	\item Add chopped tomatoes with their juices. 
	\item Turn over all ingredients and adjust the heat to cook at a slow simmer.
	\item Put a lid slightly ajar over the pot and simmer until the chicken is tender, about 20 minutes.
	\item The sauce should be slightly thickened.
	\item Off the heat stir the butter and serve immediately.
	\end{itemize}

	\end{enumerate}
\end{description}
\end{document}



