\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Popcorn}
\chead{\recipeName}

\begin{document}
\input{title}

\begin{flushright}
{\hspace{4in} From Cooks Country.}
\end{flushright}
\vspace{0.5in}

You probably never thought that your needed a recipe for popcorn. I did not think that I needed it either. But after executing this recipe many times, I now know that I needed it. Follow the recipe exactly, and make sure to measure the ingredients correctly.


\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item	 3 tablespoons vegetable oil
	\item 1/2 cup popcorn kernels
	\item 2 tablespoons unsalted butter, melted
	\item 1/4  teaspoon salt
	\end{itemize}

\item[Procedure:]\ \\

	\begin{itemize}
	\item Heat oil and 3 kernels in a covered large saucepan over medium-high heat until the three kernels pop. 
	\item Remove pan from heat, add remaining kernels, cover, and let sit for 30 seconds.
	\item Return pan to medium-high heat. 
	\item Continue cooking with lid slightly ajar until popping slows to about 2 seconds between pops. 
	\item Meanwhile melt the two tablespoons of butter. I prefer to melt the butter in a small saucepan over medium heat. 
	\item Transfer popcorn to large bowl. 
	\item Drizzle half of the melted butter over the popcorn.
	\item Toss with two large spoons.
	\item  Drizzle the remaining melted butter over the popcorn and toss again.
	\item Sprinkle one third of the salt, toss, and repeat until all salt is incorporated.
	\item Serve.
	\end{itemize}
\end{description}
\end{document}



