\documentclass [11pt, letterpaper] {article}
\input {headings}
\newcommand \recipeName {Pumpkin Spice Pumpkin Cake}
\chead {\recipeName}

\begin {document}
\input {title}

Another dairy-free cake. This one I adapted from Natasha's Kitchen (http://natashaskitchen.com/2015/11/06/easy-pumpkin-cake-recipe/) and from Cooks Illustrated's Pumpkin Cake with Cream Cheese Frosting. I liked Natasha's recipe for the simplicity in the method and for the moisture in the cake. I added a teaspoon of lemon juice to increase the power of the baking soda and make the cake even lighter. But I preferred the pumpkin spice combination and the use of salt in the Cooks Illustrated's version.

 
\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 2 cups all-purpose flour 
	\item 1 1/2 cups granulated sugar
	\item 1 teaspoon baking soda 
	\item 2 teaspoon baking powder
	\item 1 teaspoon salt
	\item 2 teaspoons ground cinnamon
	\item 1/4 teaspoon ground allspice
	\item 1/4 teaspoon ground ginger
	\item 3 large eggs, room temp
	\item 1 cup of vegetable oil
	\item 1 can (15 oz) of pumpkin puree (not pumpkin pie filling!)
	\item 1 teaspoon of lemon juice
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Prepare pan and oven}
	\begin{itemize}
	\item  Line a 9x13 inch pan with parchment paper. 
	\item Spray the paper with cooking spray.
	\item Turn oven on to 350 F.
	\end{itemize}
	\item {\bf Mix Dry ingredients}
	\begin{itemize}
	\item Using a clean whisk, in a large bowl mix flour, sugar, baking soda, baking powder, salt, cinnamon, allspice, and ground ginger.
	\end{itemize}
	\item {\bf Mix Wet Ingredients}
	\begin{itemize}
        		\item In a separate bowl lightly beat the eggs with the oil using the whisk.
		\item Pour in the pumpkin puree and stir.
		\item add the lemon juice.
	\end{itemize}
	\item {\bf Finish Batter and Bake}
	\begin{itemize}
	\item Mix the wet ingredients into the dry ingredients.
	\item Pour batter into prepared pan spreading it evenly with a spatula.
	\item Bake at 350F for approximately 35 minutes or until a toothpick inserted in the cake comes out fairly clean.
	\item Serve warm as is.
	\item You can also serve with a warm rum or bourbon sauce.
	\item You can let the cake cool completely and frost it with cream cheese frosting.
 	\end{itemize}
     	\end{enumerate}         
\end{description}
\end{document}



