\documentclass [11pt, letterpaper] {article}
\input {headings}
\newcommand \recipeName {Red Lentil Soup}
\chead {\recipeName}

\begin {document}
\input {title}

\begin{flushright}
From {\it America's Test Kitchen}
\end{flushright}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 4	tablespoons unsalted butter
	\item 1	large onion, chopped fine
	\item Salt and pepper
	\item	3/4 teaspoon ground coriander
	\item 1/2 teaspoon ground cumin
	\item 1/4 teaspoon ground ginger
	\item 1/8 teaspoon ground cinnamon
	\item Pinch cayenne
	\item 1 tablespoon tomato paste
	\item 1 garlic clove, minced
	\item 4 cups chicken broth
	\item 2 cups water
	\item 10 1/2 ounces (1 1/2 cups) red lentils, picked over and rinsed
	\item 2 tablespoons lemon juice, plus extra for seasoning
	\item 1 1/2 teaspoons dried mint, crumbled
	\item 1 teaspoon paprika
	\item 1/4 cup chopped fresh cilantro
	\end{itemize}

\item[Procedure:]\ \\
	\begin{description}
	\item[Prepare the Base]\ \\
		\begin{itemize}
			\item	Melt 2 tablespoons butter in large saucepan over medium heat. 
			\item Add onion and 1 teaspoon salt and cook, stirring occasionally, until softened but not browned, about 5 minutes.
			\item Add coriander, cumin, ginger, cinnamon, cayenne, and 1/4 teaspoon pepper and cook until fragrant, about 2 minutes. 
			\item Stir in tomato paste and garlic and cook for 1 minute. 
			\item Stir in broth, water, and lentils and bring to simmer. Simmer vigorously, stirring occasionally, until lentils are soft and about half are broken down, about 15 minutes.
		\end{itemize}
	\item[Cream the Soup]\ \\
		\begin{itemize}
			\item Whisk soup vigorously until it is coarsely pureed, about 30 seconds. 
			\item Stir in lemon juice and season with salt and extra lemon juice to taste. 
			\item Cover and keep warm. (Soup can be refrigerated for up to 3 days. Thin soup with water, if desired, when reheating.)
		\end{itemize}
	\item[Garnish the Soup]\ \\
		\begin{itemize}
			\item Melt remaining 2 tablespoons butter in small skillet. 
			\item Remove from heat and stir in mint and paprika. 
			\item Ladle soup into individual bowls, drizzle each portion with 1 teaspoon spiced butter, sprinkle with cilantro, and serve.
		\end{itemize}
	\end{description}
\end{description}
\end{document}
