\documentclass [11pt, letterpaper] {article}
\input {headings}
\newcommand \recipeName {Roasted Squash}

\chead {\recipeName}

\begin {document}
\input {title}

\begin{flushright}
Adapted from {\it America's Test Kitchen}
\end{flushright}

America's Test Kitchen created their recipe based on one from famous chef Ottolenghi. Here I am adapting it to impart some Brazilian flavours to the squash. 

\vspace{0.3in}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 1 large (2 1/2 to 3-pound) butternut squash
	\item 3 Tablespoons unsalted butter, melted
	\item 1/2 teaspoon salt
        \item  1 teaspoon ground coriander
        \item  2 pimenta de cheiro
        \item 3 additional tablespoons of unsalted butter, melted
	\item 2 inches of fresh ginger grated
	\item	cilantro
	\item 1 Tablespoon of lime juice
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}
	\item {\bf Prepping the Squash}
	\begin{itemize}
	\item Using sharp vegetable peeler or chef's knife, remove skin and fibrous threads from squash just below skin (peel until squash is completely orange with no white flesh remaining, roughly 1/8 inch deep). 
	\item Halve squash lengthwise and scrape out seeds. Place squash, cut side down, on cutting board and slice crosswise 1/2 inch thick.
	\item Put squash in a large bowl, toss squash with salt and let it sit for half hour
	\end{itemize}
	
	\item {\bf Prep the Squash}
	\begin{itemize}
	\item Preheat oven to 425 F and place a light-colour roasting pan in the oven.
	\item Mince the two pimenta de cheiro very finely.
	\item Melt 3 tablespoons of butter and mix well with the minced pimenta de cheiro and the ground coriander.
	\item Drain any liquid that accumulated in the squash bowl.
	\item Toss the squash with the seasoned melted butter.
	\end{itemize}
	
	\item {\bf Roast the Squash}
	\begin{itemize}	
	\item Remove hot roasting pan from the oven and dump the squash in it, arranging it in a single layer. 
	\item Roast squash until side touching sheet toward back of oven is well browned, 25 to 30 minutes. 
	\item Rotate sheet and continue to bake until side touching sheet toward back of oven is well browned, 6 to 10 minutes. 
	\item Remove squash from oven and use metal spatula to flip each piece. 
	\item Continue to roast until squash is very tender and side touching sheet is browned, 10 to 15 minutes longer.
	\end{itemize}
		
	\item {\bf Finish Seasoning}
	\begin{itemize}
	\item Grate the ginger using a ginger grater to make a liquid paste, avoid long ginger fibres in the paste.
	\item Mince the cilantro.
	\item Melt the additional three tablespoons of butter.
	\item Add the grated ginger, minced cilantro, tablespoon of lemon juice to the melted butter and mix well.
	\item Drizzle the seasoned butter on top of the roasted squash and toss it well.
	\item Sprinkle more minced cilantro over the squash.
	\end{itemize}
	\end{enumerate}
\end{description}

\end{document}



