\documentclass [11pt, letterpaper] {article}
\input {headings}
\newcommand \recipeName {Romeu e Julieta}
\chead {\recipeName}

\begin {document}
\input {title}

In the 1970's Mauricio de Sousa, the most successful Brazilian cartoonist responsible for "Turma da Monica" was hired to create a publicity campaign for "Goiabada da CICA." Goiabada is a sweet guava paste that is popular in Brazil. The campaign featured the pairing of the very sweet goiabada with a salty fresh cheese. Mauricio's idea was to call the sweet Goiabada "Julieta" and the salty cheese "Romeu". The  dessert "Romeu e Julieta" was popularized and is still know by this name all over Brazil. Here we work on a reinterpretation from the glitztv website~\footnote{http://www.glitztv.com.br/noticias-br/romeu-e-julieta-ganha-versao-com-queijo-mascarpone/} based on marcarpone cheese.

\vspace{0.3in}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 200 grams of goiabada
	\item 200 ml of water
	\item	200 grams of mascarpone cheese
	\item 200 grams of heavy cream
	\item 1 large pinch of salt
	\item toasted almond slivers for decoration
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}
	\item {\bf Preparing the goiabada}
	\begin{itemize}
	\item Cut the goiabada in small cubes and put in a medium size heavy-bottom saucepan.
	\item Add 200 ml of water.
	\item Cook over slow heat stirring from time to time until you obtain a thick sirupy and homogeneous paste.
	\item Let it cool to room temperature.
	\end{itemize}
	
	\item {\bf Toast the slivered almonds}
	\begin{itemize}
	\item Toast the slivered almonds in a 300 F oven watching frequently so that they turn a golden colour but do not become bitter.
	\end{itemize}
	
	\item {\bf Prepare the mousse}
	\begin{itemize}
	\item Put the mascarpone cheese, the heavy cream, and the salt in the bowl of a standing mixer.
	\item Mix to a mousse consistency.
	\item Taste for salt, the cheese mousse should be lightly salty to contrast with the sweet goiabada.
	\end{itemize}
	
	\item {\bf Serve}
	\begin{itemize}
	\item Serve in martini glasses with the goiabada in the bottom of the grass and a large spoon of the mousse floating on it.
	\item Decorate with the toasted slivered almonds.
	\end{itemize}

	\end{enumerate}
\end{description}
\end{document}



