\documentclass [11pt, letterpaper] {article}
\input {headings}
\newcommand \recipeName {Soft Pizza Dough}
\chead {\recipeName}

\begin {document}
\input {title}

At home we prefer the soft pizza dough that is more typical of the Chicago-style deep pizza. In this recipe I have replaced all dairy ingredients for dairy-free ones. If you do not have a dairy restriction, you can use  butter instead of shortening.

\vspace{0.3in}

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 10 ounces of water 
	\item 1 teaspoon sugar
	\item 1/2 teaspoon salt
	\item 2 tablespoons shortening,
	\item 2 1/2 cups flour  (12 1/2 ounces)
	\item 1 tablespoon yeast
	\end{itemize}

\item[Procedure:]\ \\

	\begin{enumerate}
	\item {\bf Preparing the dough}
	\begin{itemize}
	\item If using the bread machine, put all ingredients in the pan and set it in the dough cycle.
	\item If using a standing mixer, put the almond milk, sugar, salt in the bowl.
	\item Melt the shortening, add to the milk and stir.
	\item Add the yeast and the flour and mix using the paddle attachment until you have a soft dough.
	\item Remove the paddle, cover the bowl, and let it rise for 1 hour to 1.5 hours or until it has doubled in volume.
	\end{itemize}
	
	\item {\bf Preparing the dough for the pizza}
	\begin{itemize}
	\item This is a very wet dough, thus you may need to incorporate additional flour now to form individual pizzas.
	\item Dump the dough in a well-floured surface and punch the dough to eliminate air bubbles and knead it. Be careful to not over work the dough.
	\item Form the pizzas and let them rise for at least 30 minutes before topping and baking.
	\item Alternatively you can press the wet dough into a pan that you have been oiled with olive oil --- use oils in your hands too --- and let it rise in the pan.
	\item If you are cooking the pizza in a baking pan, pre-heat the oven to 350 F and bake the dough without any toppings for 20 minutes. Remove from the oven, add the toppings, and return to the oven. 
	\end{itemize}
	
	\end{enumerate}
\end{description}
\end{document}



