\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Harissa Spiced Lentils with Pumpkin}
\chead{\recipeName}

\begin{document}
\input{title}

This is a recreation of a recipe by Tess Mallos that I found in {\it The food of Morocco: a journey for food lovers}. The original recipe was cooked in a stew style. It was possible, but tricky, to produce a final result with the pumpkin and the lentils with right consistency. Moreover, the original recipe used brown lentils which have a tendency to turn mushy if even slightly overcooked. I replaced them with lentil Dupuy which are more forgiving and more tasty. My version of the recipe cooks the tomato sauce and the lentils separately, and also roasts the pumpkin. The dish is assembled before serving so that the components retain their individual flavour profiles as is the modern expectations.

\begin{description}

\item[Ingredients:]\ \\
	\begin{itemize}
	\item 1 \href{MoroccanRoastedButternutSquash.html}{Moroccan Roasted Butternut Squash} recipe
	\item 1 \href{HarissaTomatoSauce.html}{Harissa Tomato Sauce} recipe
	\item 500 grams of lentil dupuy 
	\item 1 teaspoon of salt
	\item 2 tablespoons of chopped cilantro
	\end{itemize}

\item[Procedure:]\ \\
	\begin{itemize}
	\item Wash the lentils in cold water and rinse twice 
	\item Soak the lentils in cold water for at least one hour. They can be soaked overnight.
	\item Cook the lentils over moderate heat for about 30 minutes until they are cooked but still very firm. 
	\item Once the lentils are cooked, add the salt and let seat for fifteen minutes
	\item Drain the lentils.
	\item Gently fold the drained lentils with the warm tomato sauce.
	\item Spread the lentils with tomato sauce on a serving dish.
	\item Sprinkle the roasted pumpkin on top of the lentils.
	\item Sprinkle with the chopped cilantro
	\end{itemize}
\end{description}
\end{document}
