\documentclass[11pt,letterpaper]{article}
\input{headings}
\newcommand \recipeName {Tangine Kefta 'Mchermel}
\chead{\recipeName}

\begin{document}
\input{title}

This is a delicious Moroccan dish of meatballs with herbs and lemon. This recipe can be made with beef, lamb, or a combination of both.

\begin{description}

\item[Meatball Ingredients:]\ \\
	\begin{itemize}
	\item 1/2 onion roughly chopped
	\item 2 tablespoons of roughly chopped Italian flat-leaf parsley
	\item 2 slices of crustless white bread
	\item 1 egg
	\item 500 grams of ground lamb, beef, or a combination
	\item 1/2 teaspoon of ground cumin
	\item 1/2 teaspoon paprika
	\item 1/2 tablespoon of freshly ground black pepper
	\item 1 teaspoon of salt
	\end{itemize}
\item[Sauce Ingredients:]\ \\
	\begin{itemize}
	\item 1 tablespoon of butter or oil
	\item 1/2 brown onion, finely chopped
	\item 1/2 teaspoon paprika
	\item 1/2 teaspoon ground turmeric
	\item 1/4 teaspoon ground cumin
	\item 1 red chilli, seeded and sliced (or 1/4 teaspoon cayenne pepper)
	\item 375 ml of chicken stock or water
	\item 2 tablespoons chopped cilantro
	\item 2 tablespoons chopped Italian parsley leaves
	\item 2 tablespoons lemon juice
	\item 1 tablespoon of grated lemon zest
	\end{itemize}

\item[Procedure:]\ \\
	\begin{enumerate}
	\item {\bf Make the meat balls}
	\begin{itemize}
	\item Put the 1/2 onion and 2 tablespoons of parsley  in the food processor and process until finely chopped
	\item Tear the bread into pieces, add to the bowl with the egg and process briefly
	\item Add the meat, cumin, paprika, black paper, 1 teaspoon of salt and process until well mixed. Do not overwork the meat.
	\item With moistened hands, shape the mixture into walnut-sized balls and place them in a tray. Alternatively use a small ice-cream scoop to measure the meatballs and then form them into balls with the moistened hands. 
	\end{itemize}
	\item {\bf Make the herb and lemon sauce}
	\begin{itemize}
	\item Heat the butter or oil in a saucepan.
	\item Add the onion.
	\item Cook over low heat for eight minutes until softened.
	\item Add the paprika, turmeric, cumin and chilli or cayenne.
	\item Cook, stirring, for one minute.
	\item Add the stock and coriander and bring to a boil.
	\end{itemize}
	\item{\bf Cook meatballs in the sauce}
	\begin{itemize}
	\item Add the meatballs to the sauce.
	\item Shake the pan so that the meatballs settle in the sauce.
	\item Cover and simmer for 45 minutes.
	\item Add most of the parsley and the lemon juice and season if necessary.
	\item Return the simmer for two minutes.
	\item Add the grated lemon zest and serve.
	\end{itemize}
	\end{enumerate}
\end{description}
\end{document}
